---
title: "Within analysis and Between Model Comparison"
date: "31/03/2022"
output: html_document
---

```{r library and master file, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", include=FALSE}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(mlogit)
library(sjmisc)
library(ggrepel)
library(readxl)
library(readr)
library(sjPlot)
library(ggpubr)
library(foreign)
library(survival)
library(gridExtra)
library(kableExtra)
library(car)
library(DT)
library(zoo)
library(AICcmodavg)
library(boot)
library(arm)

setwd("../")

# read data beliefs and choices with ALL DATA
master <- read.csv("File_DB/Output/Treatment.csv") %>%
  mutate(treatment_id=paste(PaperID,TreatmentCode,sep="_"))
beliefs <- read.csv("File_DB/Output/Subjects_beliefs.csv", sep = ",")
choices <- read.csv("File_DB/Output/Subjects_choices.csv", sep = ",")

setwd("Paper_csv/")
df_avg_kw <- read.csv("2016Kim003_avg_kw.csv", sep = ",") 
df_avg_kw <- read.csv("2018Her061_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw)
df_avg_kw <- read.csv("2013Kru001_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw)
df_avg_kw <- read.csv("2019Cha026_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw)
df_avg_kw <- read.csv("2012Laz164_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw)
df_avg_kw <- read.csv("2007Lis165_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw)
df_avg_kw <- read.csv("2020Bas115_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw) 
df_avg_kw <- read.csv("2020And089_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw) %>%
  mutate(treatment_id = paste(PaperID,"_",TreatmentCode,sep=""))
```


## Bicchieri Analysis {.tabset .tabset-pills}

This analysis is performed on "Evidence from a long-term experiment that collective risks change social norms and promote cooperation". 
All rounds are included and we performed a "Fit Linear Mixed-Effects Model". The effects are "treatment_id" and "round number".

The following results show the coefficients for the experiment's first and replicated version.
The independent variables of the model are "normative expectations", "empirical expectations" and "personal normative beliefs".

I also tried to include the risk change during the experiment in this analysis. Still, the model fails to estimate variables correctly due to too many effects (treatment, round and risk). For this reason, I choose to show the model without the risk effect.

```{r bicchieri analysis, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
# BICCHIERI ANALYSIS

pgg_t <- read.csv("/Volumes/GoogleDrive/.shortcut-targets-by-id/1IoJDOQWCFiL1qTzSja6byrAlCelNSTsT/Meta-analysis beliefs/Dati paper/2021Sze167/full.csv") %>% 
  dplyr::select(treatment, id, round, excluded, contribution, contribute_cond, pnb, ee1:ee5, ee_avg, ne1:ne5, ne_avg) %>%
  filter(#round==1 &
           !(is.na(contribution)) & 
           excluded!="Excluded" &
           !(is.na(ee1))) %>%
  mutate(coop = contribution/100,
         inf_ne = ne_avg - contribution,
         inf_ee = ee_avg - contribution,
         sub_treat = ifelse(round>14,1,0))

ml.all <- lmer(contribution ~ 0 + ne_avg + ee_avg + pnb + (1|treatment) + (1 + ne_avg + ee_avg + pnb|round), pgg_t)

pgg_t_rep <- read.csv("/Volumes/GoogleDrive/.shortcut-targets-by-id/1IoJDOQWCFiL1qTzSja6byrAlCelNSTsT/Meta-analysis beliefs/Dati paper/2021Sze167/full_replicated.csv") %>%
  dplyr::select(treatment, id, round, excluded, contribution, contribute_cond, pnb, ee1:ee5, ee_avg, ne1:ne5, ne_avg) %>%
  filter(#round==1&
           !(is.na(contribution)) & 
           excluded!="Excluded" &
           !(is.na(ee1))) %>%
  mutate(coop = contribution/100,
         inf_ne = ne_avg - contribution,
         inf_ee = ee_avg - contribution,
         sub_treat = ifelse(round>14,1,0))

ml.all_rep <- lmer(contribution ~ 0 + ne_avg + ee_avg + pnb + (1|treatment) + (1 + ne_avg + ee_avg + pnb|round), pgg_t_rep)

tab_model(ml.all, ml.all_rep, dv.labels = c("First", "Replicated"), show.aic = T, show.loglik = T, show.se = T, show.ci = F, title = "First and Replicated verison - all round, effects: treatment and round", transform=NULL)
```


## Model Comparison (between studies) {.tabset .tabset-pills}
This section shows the results of the model comparison for between studies.

For each game type, we have:

 -    plot of coefficients of Social Expectation model (Krupka & Weber 2013) $U_{ik} = \delta \pi_k + \gamma N_k + \epsilon_{ik}$
 
      - $\pi_k$ : payoff
      
      - $N_k$ : norm appropriateness

 -    plot of coefficients of Social Preferencesn model (Charness & Rabin 2002) $U_{ik} = (\rho * r + \sigma * s)(W-k_i) + (1 - \rho * r - \sigma * s)k_i$
 
      -   $k_i$ : dictator's payoff
      
      -   $W$ : initial endowment
      
      -   $r=1$ if $k_i>5$, in this case, $\rho$ indicates the concern for the others only when dictator has more than the others
      
      -   $s=1$ if $k_i<5$, in this case, **$\sigma$** indicates the concern for the others only when dictator has less than the others
 
 -    plot of AIC comparison


 
```{r function and graphics, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
model_df_generator <- function(file) {
  df <- read.csv(file)

  df <- df %>%
    mutate(weight_SE=(n.x)^2) 

  average_coeff_stata <- df %>% summarise(across(deltaS:gammaFU, ~weighted.mean(., w = n.x, na.rm=T)))
  average_SE_stata <- df %>% summarise(across(se_deltaS:se_gammaFU, ~weighted.mean(.^2, w = weight_SE, na.rm=T)))
  #average_SE_stata <- df %>% summarise(across(deltaS_SE:cr_sigma_SE, ~weighted.mean(.^2, w = n_obs, na.rm=T)))

  df <- df %>%
    add_row(treatment_id="Average", average_coeff_stata , sqrt(average_SE_stata), n.x=sum(df$n.x), weight_SE=sum(df$weight_SE))

  invisible(df)
}

plot_coeff_social_generator <- function(data) {
  
  # selfish model

    plot_s_delta <- ggplot(data, aes(x=deltaS,y=treatment_id)) + 
    geom_pointrange(aes(xmin=deltaS-1.96*se_deltaS,xmax=deltaS+1.96*se_deltaS), shape=20) +
    ylab("Treatment ID") +
    xlab("S model - Coefficient of payoff (delta)") +
    theme_light() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)
  
  # Social norm model (SN)

  plot_sn_delta <- ggplot(data, aes(x=deltaN,y=treatment_id)) + 
    geom_pointrange(aes(xmin=deltaN-1.96*se_deltaN,xmax=deltaN+1.96*se_deltaN), shape=20) +
    ylab("Treatment ID") +
    xlab(expression(delta)) +
    theme_light() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)

  plot_sn_gamma <- ggplot(data, aes(x=gammaN,y=treatment_id)) + 
    geom_pointrange(aes(xmin=gammaN-1.96*se_gammaN,xmax=gammaN+1.96*se_gammaN), shape=20) +
    xlab(expression(gamma)) +
    theme_light() +
    theme(axis.text.y=element_blank(),
          axis.title.y=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)
    
  # Social preferences models

  plot_da_rho <- ggplot(data, aes(x=rhoDA,y=treatment_id)) + 
    geom_pointrange(aes(xmin=rhoDA-1.96*se_rhoDA,xmax=rhoDA+1.96*se_rhoDA), shape=20) +
    ylab("Treatment ID") +
    xlab(expression(rho)) +
    theme_light() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)

  plot_da_sigma <- ggplot(data, aes(x=sigmaDA,y=treatment_id)) + 
    geom_pointrange(aes(xmin=sigmaDA-1.96*se_sigmaDA,xmax=sigmaDA+1.96*se_sigmaDA), shape=20) +
    xlab(expression(sigma)) +
    theme_light() +
    theme(axis.text.y=element_blank(),
          axis.title.y=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)
    
  # Full model (social preferences and social norms)

  plot_fu_rho <- ggplot(data, aes(x=rhoFU,y=treatment_id)) + 
    geom_pointrange(aes(xmin=rhoFU-1.96*se_rhoFU,xmax=rhoFU+1.96*se_rhoFU), shape=20) +
    ylab("Treatment ID") +
    xlab(expression(rho)) +
    theme_light() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)

  plot_fu_sigma <- ggplot(data, aes(x=sigmaFU,y=treatment_id)) + 
    geom_pointrange(aes(xmin=sigmaFU-1.96*se_sigmaFU,xmax=sigmaFU+1.96*se_sigmaFU), shape=20) +
    xlab(expression(sigma)) +
    theme_light() +
    theme(axis.text.y=element_blank(),
          axis.title.y=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)
  
  plot_fu_gamma <- ggplot(data, aes(x=gammaFU,y=treatment_id)) + 
    geom_pointrange(aes(xmin=gammaFU-1.96*se_gammaFU,xmax=gammaFU+1.96*se_gammaFU), shape=20) +
    xlab(expression(gamma)) +
    theme_light() +
    theme(axis.text.y=element_blank(),
          axis.title.y=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)
    
  plot_sn <- ggarrange(plot_sn_delta, plot_sn_gamma, common.legend=T, legend="bottom", widths = c(8,6))
  plot_sn <- annotate_figure(plot_sn, top = text_grob("Social Norm model", face = "bold", size = 14))
  plot_da <- ggarrange(plot_da_rho, plot_da_sigma, common.legend=T, legend="bottom", widths = c(8,6))
  plot_da <- annotate_figure(plot_da, top = text_grob("Social Preferences model", face = "bold", size = 14))
  plot_fu <- ggarrange(plot_fu_rho, plot_fu_sigma, plot_fu_gamma, nrow = 1, common.legend=T, legend="bottom", widths = c(9,6,6))
  plot_fu <- annotate_figure(plot_fu, top = text_grob("Full model", face = "bold", size = 14))
  #final_plot <- ggarrange(plot_sn, plot_da, plot_fu, ncol = 1)
  ggsave(filename = "model_social_norm.png", plot = plot_sn)
  ggsave(filename = "model_social_preferences.png", plot=plot_da)
  ggsave(filename = "model_full.png", plot=plot_fu)
  
  return(list(plot_sn, plot_da, plot_fu))
}
```


```{r function and graphics, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
plot_coeff_charness_generator <- function(data){
  plot_cr_rho <- ggplot(data, aes(x=cr_rho,y=treatment_id)) + 
    geom_pointrange(aes(xmin=cr_rho-1.96*cr_rho_SE,xmax=cr_rho+1.96*cr_rho_SE), shape=20) +
    ylab("Treatment ID") +
    xlab("Rho") +
    theme_light() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)
  
  plot_cr_sigma <- ggplot(data, aes(x=cr_sigma,y=treatment_id)) + 
    geom_pointrange(aes(xmin=cr_sigma-1.96*cr_sigma_SE,xmax=cr_sigma+1.96*cr_sigma_SE), shape=20) +
    ylab("Treatment ID") +
    xlab("Sigma") +
    theme_light() +
    theme(axis.text.y=element_blank(),
          axis.title.y=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_vline(xintercept = 0)
    
  plot <- ggarrange(plot_cr_rho, plot_cr_sigma, ncol = 2, common.legend=T, legend="bottom", widths = c(8,6))
  final_plot <- annotate_figure(plot, top = text_grob("Social Preferences Model (Charness and Rabin 2002)", face = "bold", size = 14))

  return(final_plot)
}

plot_aic_generator <- function(data){
  plot <- ggplot(data = data, aes(Delta_se_cr, treatment_id)) + 
    geom_col(aes(fill=Best_model_se_cr)) + 
    xlim(-max(abs(data$Delta_se_cr))*1.2,max(abs(data$Delta_se_cr))*1.2) +
    xlab("AIC Delta") +
    ylab("Treatment") +
    theme_light() +
    theme(legend.position="bottom",
          strip.text.x = element_text(size = 12, color = "black", face = "bold.italic"),
          strip.background = element_blank()) +
    scale_fill_brewer(palette="Set1") + 
    geom_point(shape=1) +
    geom_vline(xintercept = 0)
  
  final_plot <- annotate_figure(plot, top = text_grob("AIC comparison - Social expectation vs Charness & Rubin", face = "bold", size = 14))

  return(final_plot)
}
```

### Dictator Game

```{r dictator, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
stata_output_model <- model_df_generator("Utility estimation/Output/Logs/MODEL_DG.csv")
#stata_aic <- read_excel("stata aic DG.xlsx") %>%
#  mutate(Best_model_se_cr=ifelse(Delta_se_cr<0,"Social Expectation", "Charness & Rabin"))

plot_coeff_social_generator(stata_output_model)
#plot_coeff_charness_generator(stata_output_model)
#plot_aic_generator(stata_aic)
```

### Take or Give
```{r tog, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
stata_output_model <- model_df_generator("stata output model ToG.xlsx")
stata_aic <- read_excel("stata aic ToG.xlsx") %>%
  mutate(Best_model_se_cr=ifelse(Delta_se_cr<0,"Social Expectation", "Charness & Rabin"))

plot_coeff_social_generator(stata_output_model)
plot_coeff_charness_generator(stata_output_model)
plot_aic_generator(stata_aic)
```

### Donation Game
```{r donation, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
stata_output_model <- model_df_generator("stata output model DON.xlsx")
stata_aic <- read_excel("stata aic DON.xlsx") %>%
  mutate(Best_model_se_cr=ifelse(Delta_se_cr<0,"Social Expectation", "Charness & Rabin"))

plot_coeff_social_generator(stata_output_model)
plot_coeff_charness_generator(stata_output_model)
plot_aic_generator(stata_aic)
```

## STATA LOG FILE READING 
```{r read log AIC, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
#QUESTO SCRIPT LEGGE IL FILE LOG AIC DA STATA
## MODIFICARE SUFFISSO "_DG" CON "_ToG" O "_DON"
## MODIFICARE n_max = x, x È UGUALE AL NUMERO DI TRATTAMENTI

log_file = "~/GitHub/Social_norm_meta_analysis/Analysis/Utility estimation/Output/Logs/stata_AIC_ONG.log"
df_aic <- read_log(file=log_file,
               skip=10,
               n_max = 9)
colnames(df_aic) <- c("treatment_id", "Selfish_aic", "Norm_aic", "DA_aic", "FU_aic")

avg_aic <- df_aic %>% 
  summarise(across(Selfish_aic:FU_aic, ~mean(., na.rm=T)))

df_aic <- df_aic %>%
    add_row(treatment_id="Average", avg_aic)

write.csv(df_aic, "~/GitHub/Social_norm_meta_analysis/Analysis/Utility estimation/Output/Logs/AIC_DG.csv", row.names = F)
```

```{r read log COEFF and STDDEV, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
#QUESTO SCRIPT LEGGE IL FILE LOG COEFF DA STATA
## MODIFICARE SUFFISSO "_DG" CON "_ToG" O "_DON"
## MODIFICARE n_max = x, x è UGUALE AL NUMERO DI TRATTAMENTI

log_file = "~/GitHub/Social_norm_meta_analysis/Analysis/Utility estimation/Output/Logs/stata_COEFF_ONG.log"
df_coeff <- read_log(file=log_file,
               skip=10,
               n_max = 9,
               col_types=cols("c","n","n","n","n","n","n","n","n","n","n","n","n"))

colnames(df_coeff) <- c("treatment_id", "deltaS", "deltaN", "gammaN", "rhoDA", "sigmaDA", "rhoFU", "sigmaFU", "gammaFU")

observation <- read.csv("new_data_utility.csv") %>% distinct(treatment_id,subject_id,Game_type) %>% group_by(treatment_id,Game_type) %>% tally()

df_coeff <- df_coeff %>%
  merge.data.frame(observation, by = "treatment_id")

avg_coeff <- df_coeff %>% 
  summarise(across(deltaS:gammaFU, ~weighted.mean(., w = n, na.rm=T)))

df_coeff <- df_coeff %>%
    add_row(treatment_id="Average", avg_coeff, n=sum(df_coeff$n), Game_type="DG")

#QUESTO SCRIPT LEGGE IL FILE LOG STD ERR DA STATA

log_file = "~/GitHub/Social_norm_meta_analysis/Analysis/Utility estimation/Output/Logs/stata_SE_ONG.log"
df_se <- read_log(file=log_file,
               skip=10,
               n_max = 9,
               col_types=cols("c","n","n","n","n","n","n","n","n","n","n","n","n"))

colnames(df_se) <- c("treatment_id", "se_deltaS", "se_deltaN", "se_gammaN", "se_rhoDA", "se_sigmaDA", "se_rhoFU", "se_sigmaFU", "se_gammaFU")

df_se <- df_se %>%
  merge.data.frame(observation, by = "treatment_id") %>%
  mutate(weight_SE=n^2)

avg_se <- df_se %>% 
  summarise(across(se_deltaS:se_gammaFU, ~weighted.mean(.^2, w = weight_SE, na.rm=T)))

df_se <- df_se %>%
    add_row(treatment_id="Average", sqrt(avg_se), n=sum(df_se$n), weight_SE=sum(df_se$weight_SE))

df_models <- merge.data.frame(df_coeff, df_se, by = "treatment_id")

write.csv(df_models, "~/GitHub/Social_norm_meta_analysis/Analysis/Utility estimation/Output/Logs/MODEL_DG.csv", row.names = F)

```
