---
title: "dg_analysis"
author: "Sp & AG"
date: "19/1/2022"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", include=FALSE}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(mlogit)
library(sjmisc)
library(ggrepel)
library(readxl)
library(ggpubr)
library(survival)
library(gridExtra)
library(sjPlot)
library(kableExtra)
library(car)
library(DT)
library(zoo)

setwd("../")
# read data 
getwd()
master <- read.csv("File_DB/Output/Treatment.csv") %>% 
  filter(Game_type == "DG") %>%
  subset.data.frame(subset = !(Standard_game %in% c("N")) & Choice_Method != "OnlyNorms" & StatusTreatment_Roma == "6-Complete" & Baseline %in% c(NA, 1))

list_of_paper_in_target <- read.csv("File_DB/Output/Treatment.csv") %>% 
  filter(Game_type == "DG") %>%
  subset.data.frame(subset = !(Standard_game %in% c("N")) & Choice_Method != "OnlyNorms" & StatusTreatment_Roma == "6-Complete" & Baseline %in% c(NA, 1), select = c(PaperID, TreatmentCode, TreatmentName_paper, Year, Game_type, Standard_game, Baseline, Group_size, Rounds, Method_elicitation, Avg_coop, Avg_NE, Var_coop, Var_NE, Avg_KW_m))

beliefs <- read.csv("File_DB/Output/Subjects_beliefs.csv", sep = ",") %>%
  filter(treatment_id %in% levels(as.factor(paste(master$PaperID,"_",master$TreatmentCode, sep=""))))
choices <- read.csv("File_DB/Output/Subjects_choices.csv", sep = ",") %>%
  filter(treatment_id %in% levels(as.factor(paste(master$PaperID,"_",master$TreatmentCode, sep=""))))

```

# Description of data included

## Search criteria

The selection criteria to identify papers in target was:

* **Game type** (cooperation and prosociality games):
  + Dictator Game <!--(with tax/standard/Lying); -->
  <!-- + Donation Game; -->
  <!-- + Ultimatum Game; -->
  <!-- + Trust Game; -->
  <!-- + Public Good Game; -->
  <!-- + Prisoner's Dilemma Game; -->
  <!-- + Take or Give Fame; -->
  <!-- + CPR; -->
  <!-- + Bargaining Game; -->
  <!-- + Tax Game; -->
  <!-- + Investment Game; -->
* Presence of norm elicitation task:
  + Krupka and Weber (2013);
  + Bicchieri-Xiao (2009).
* Only monetary incentivized studies (both choices and norms elicitation).
* Baseline treatment (no framing)
* Standard game
* Both choice and normative task
* Data available

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

opts <- options(knitr.kable.NA = "")
kbl(list_of_paper_in_target, digits = 4, booktabs = T, align = "llllllllllrrrrrr", centering = F, caption="List of paper after selection criteria applied") %>%
  kable_styling(position = "left", full_width = F) %>%
  column_spec(1, bold = T)

```

## Plots

Beliefs

```{r}
setwd("../")
setwd("Paper_csv/")
getwd()

df_avg_kw <- read.csv("2016Kim003_avg_kw.csv", sep = ",") 
df_avg_kw <- read.csv("2018Her061_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw)
df_avg_kw <- read.csv("2019Cha026_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw)
df_avg_kw <- read.csv("2020Bas115_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw) %>%
  mutate(treatment_id = paste(PaperID,"_",TreatmentCode,sep=""))

df_avg_kw <-  df_avg_kw %>% merge.data.frame(master %>% subset.data.frame(select = c(PaperID, TreatmentName_paper, TreatmentCode)) %>% mutate(treatment_id = paste(PaperID,"_",TreatmentCode,sep="")), by = c("PaperID","TreatmentCode","treatment_id")) %>% filter(!(is.na(TreatmentName_paper)))
temp_master <- df_avg_kw %>% distinct(treatment_id)

n=1
list_plot <-  c()
for (i in temp_master$treatment_id) {
  temp_master_for <- df_avg_kw %>% filter(treatment_id == i)
  list_plot[[n]] <- ggplot(temp_master_for, aes(x=donation, y=Kw_m)) + 
    geom_bar(stat = "identity") + 
    labs(title = i, subtitle = temp_master_for$TreatmentName_paper[temp_master_for$treatment_id == i]) +
    ylim(-1,1) +
    xlab("Scenario") + 
    ylab("Appropriateness (average)")
  n=n+1
}

do.call('grid.arrange',c(list_plot, ncol = 2))
```

Choices

```{r}
perc_choices <- choices %>% filter(A==1) %>% group_by(treatment_id, choice) %>% summarise(n_of_sub = n())
sum(perc_choices$n_of_sub)-nrow(choices %>% filter(A==1))

perc_choices <-  perc_choices %>% merge.data.frame(master %>% subset.data.frame(select = c(PaperID, TreatmentName_paper, TreatmentCode)) %>% mutate(treatment_id = paste(PaperID,"_",TreatmentCode,sep="")), by = "treatment_id") %>% filter(!(is.na(TreatmentName_paper)))

temp_master <- choices %>% distinct(treatment_id)

n=1
list_plot <-  c()
for (i in temp_master$treatment_id) {
  temp_master_for <- perc_choices %>% filter(treatment_id == i)
  temp_master_for <- temp_master_for %>% mutate(total = sum(n_of_sub), perc_per_action = round(n_of_sub/total*100, digits=2))
  list_plot[[n]] <- ggplot(temp_master_for, aes(x=choice, y=perc_per_action)) + 
    geom_bar(stat = "identity") + 
    labs(title = i, subtitle = temp_master_for$TreatmentName_paper[temp_master_for$treatment_id == i]) + 
    ylim(0,100) +
    xlab("Choice") + ylab("Subjects (%)")
  n=n+1
}

do.call('grid.arrange',c(list_plot, ncol = 2))
```





# Individual-level analyses

```{r}
# belief dataset aggregated to get appropriateness for each action
beliefs_temp <- beliefs %>% subset.data.frame(subset = Design=="Between"&Game_type=="DG") %>% group_by(paper_id, treatment_id,scenarios) %>% summarise(avg_kw = mean(KW_Normative, rm.na=T),
                                                                                                                                                       sd_kw = sd(KW_Normative, na.rm = T))
Kim003_interpolation <- beliefs_temp %>% subset.data.frame(paper_id == "2016Kim003" & treatment_id == "2016Kim003_7") %>%
  rbind.data.frame(data.frame(paper_id="2016Kim003", treatment_id="2016Kim003_7", scenarios=seq(1,15,2), avg_kw=NA, sd_kw=NA)) %>%
  ungroup() %>% arrange(scenarios) %>%
  mutate(KW_Normative = na.approx(avg_kw, maxgap = 1, rule = 1),
         sd_KW = na.approx(sd_kw, maxgap = 1, rule = 1))
mean_beliefs <- beliefs %>% merge.data.frame(Kim003_interpolation, all = T) %>% group_by(paper_id, treatment_id, scenarios) %>% summarise(mean_app=mean(KW_Normative), sd_app=mean(sd_KW))
individual_db <- choices %>% merge.data.frame(mean_beliefs)%>% mutate(payoff=endowment-scenarios)
master$treatment_id = paste(master$PaperID,"_",master$TreatmentCode, sep="")
# mlogit
for (i in levels(as.factor(individual_db$treatment_id))) {
  model=mclogit::mclogit(cbind(A,choice)~ payoff + mean_app + sd_app, data=individual_db%>% filter(treatment_id==i))
  print(i)
print(summary(model))
}
#mdata=mlogit.data(individual_db, chid.var = "scenarios")
#mlogit()
```

