---
title: "dg_analysis"
author: "Sp & AG"
date: "25/1/2022"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", include=FALSE}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(mlogit)
library(sjmisc)
library(ggrepel)
library(readxl)
library(sjPlot)
library(ggpubr)
library(survival)
library(gridExtra)
library(kableExtra)
library(car)
library(DT)
library(zoo)

setwd("../")

# read data 
master <- read.csv("File_DB/Output/Treatment.csv") %>% 
  filter(Game_type == "DG") %>%
  subset.data.frame(subset = !(Standard_game %in% c("N")) & 
                      Choice_Method != "OnlyNorms" & 
                      StatusTreatment_Roma == "6-Complete" & 
                      Baseline %in% c(NA, 1)) %>% 
  mutate(treatment_id = paste(PaperID,"_",TreatmentCode,sep=""))

# list of treatments in target
list_of_paper_in_target <- read.csv("File_DB/Output/Treatment.csv") %>% 
  filter(Game_type == "DG") %>%
  subset.data.frame(subset = !(Standard_game %in% c("N")) & 
                      Choice_Method != "OnlyNorms" & 
                      StatusTreatment_Roma == "6-Complete" & 
                      Baseline %in% c(NA, 1), 
                    select = c(PaperID, TreatmentCode, TreatmentName_paper, 
                               Year, Game_type, Standard_game, 
                               Baseline, Group_size, Rounds, 
                               Method_elicitation, Avg_coop, Avg_NE, 
                               Var_coop, Var_NE, Avg_KW_m))

# read file beliefs and choices
beliefs <- read.csv("File_DB/Output/Subjects_beliefs.csv", sep = ",") %>%
  filter(treatment_id %in% levels(as.factor(paste(master$PaperID,"_",master$TreatmentCode, sep=""))))

choices <- read.csv("File_DB/Output/Subjects_choices.csv", sep = ",") %>%
  filter(treatment_id %in% levels(as.factor(paste(master$PaperID,"_",master$TreatmentCode, sep=""))))

```

# Description of data included

## Search criteria

The selection criteria to identify papers in target was:

* **Game type** (cooperation and prosociality games):
  + Dictator Game
* Presence of norm elicitation task:
  + Krupka and Weber (2013);
* Only monetary incentivized studies (both choices and norms elicitation).
* Baseline treatment (no framing)
* Standard game
  + Not a minigame
  + Two players
  + No papers that give the recipient any kind of power (and thereby bring the experiment close to an ultimatum game);
  + No papers that mix the motive of benevolence with one of sanctioning the recipient
  + No papers that limit the dictator’s action space such that it does not include the option to give nothing nor to take from the recipient
  + No real effort task used to determine the dictator’s endowment
* Both choice and normative task
* Data available

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

# print table of "list_of_paper_in_target"
opts <- options(knitr.kable.NA = "")
kbl(list_of_paper_in_target,
    digits = 4, 
    booktabs = T, 
    align = "llllllllllrrrrrr", 
    centering = F, 
    caption="List of paper after selection criteria applied") %>%
  kable_styling(position = "left", 
                full_width = F) %>%
  column_spec(1, bold = T)
```

# Plots {.tabset}
<!-- tab: beliefs, choices -->

## Beliefs

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
setwd("../")
setwd("Paper_csv/")

df_avg_kw <- read.csv("2016Kim003_avg_kw.csv", sep = ",") 
df_avg_kw <- read.csv("2018Her061_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw)
df_avg_kw <- read.csv("2019Cha026_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw)
df_avg_kw <- read.csv("2020Bas115_avg_kw.csv", sep = ",") %>% rbind.data.frame(df_avg_kw) %>%
  mutate(treatment_id = paste(PaperID,"_",TreatmentCode,sep=""))

df_avg_kw <-  df_avg_kw %>% merge.data.frame(master %>% 
                                               subset.data.frame(select = c(PaperID, 
                                                                            TreatmentName_paper, 
                                                                            TreatmentCode, 
                                                                            treatment_id)), 
                                             by = c("PaperID","TreatmentCode","treatment_id")) %>% 
  filter(!(is.na(TreatmentName_paper)))
temp_master <- df_avg_kw %>% 
  distinct(treatment_id)

# inizializing variable for loop
n=1
list_plot <- c()

# creation of a plots list
for (i in temp_master$treatment_id) {
  
  # dataset
  temp_master_for <- df_avg_kw %>% 
    filter(treatment_id == i)
  
  # list
  list_plot[[n]] <- ggplot(temp_master_for, 
                           aes(x=donation, y=Kw_m)) + 
    geom_bar(stat = "identity") + 
    labs(title = i, 
         subtitle = temp_master_for$TreatmentName_paper[temp_master_for$treatment_id == i]) +
    ylim(-1,1) +
    xlab("Scenario") + 
    ylab("Appropriateness (average)")
  
  n=n+1
}

# merge plots in one figure
do.call('grid.arrange', 
        c(list_plot, ncol = 2))
```

## Choices

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
# dataset
perc_choices <- choices %>% 
  filter(A==1) %>% 
  group_by(treatment_id, choice) %>% 
  summarise(n_of_sub = n(),
            endowment = mean(endowment)) %>%
  merge.data.frame(master %>% 
                     subset.data.frame(select = c(PaperID, TreatmentName_paper, 
                                                  TreatmentCode, treatment_id)), 
                   by = "treatment_id") %>% 
  filter(!(is.na(TreatmentName_paper)))

temp_master <- choices %>% 
  distinct(treatment_id)

# inizializing variables for loop
n=1
list_plot <- c()

# creation of a plots list
for (i in temp_master$treatment_id) {
  
  # dataset
  temp_master_for <- perc_choices %>% 
    filter(treatment_id == i)
  temp_master_for <- temp_master_for %>% 
    mutate(total = sum(n_of_sub), 
           perc_per_action = round(n_of_sub/total*100, digits=2))
  print(temp_master_for$endowment)
  # list
  list_plot[[n]] <- ggplot(temp_master_for, 
                           aes(x=choice, 
                               y=perc_per_action)) + 
    geom_bar(stat = "identity") + 
    labs(title = i, 
         subtitle = temp_master_for$TreatmentName_paper[temp_master_for$treatment_id == i]) +
    xlim(-1,temp_master_for$endowment[1]) +
    ylim(0,100) +
    xlab("Choice") + 
    ylab("Subjects (%)")
  
  n=n+1
}

# merge plots in one figure
do.call('grid.arrange',c(list_plot, ncol = 2))
```

# Consistency and Specificity {.tabset}
<!-- tab: consistency, specificity -->

## Formulas

$$ consistency = \frac{1}{\sigma_n}$$

$$ specificity = \frac{\#\ of\ negative\ actions}{\#\ of\ positive\ actions}$$

## Consistency

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
# interpolation of appropriateness with scenarios out of game
beliefs_only_kim <- beliefs %>%
  filter(paper_id == "2016Kim003" & treatment_id == "2016Kim003_7") %>%
  select(paper_id, treatment_id, subject_id, scenarios, KW_Normative) %>%
  mutate(KW_Normative_temp = KW_Normative)

n_subj = length(levels(as.factor(beliefs_only_kim$subject_id)))

kim003_interpolation <- data.frame(paper_id=NA,
                           treatment_id=NA,
                           subject_id = NA,
                           scenarios=NA,
                           KW_Normative=NA,
                           KW_Normative_temp=NA)

for (subj in levels(as.factor(beliefs_only_kim$subject_id))) {
  subj_df <- data.frame(paper_id="2016Kim003",
                        treatment_id="2016Kim003_7",
                        subject_id = subj,
                        scenarios=seq(1,15,2),
                        KW_Normative = NA,
                        KW_Normative_temp=NA)
  
  subj_beliefs <- beliefs_only_kim %>%
    filter(subject_id == subj)
  #print(subj_beliefs)
  
  subj_beliefs <- subj_beliefs %>%
    rbind.data.frame(subj_df) %>%
    arrange(paper_id, treatment_id, subject_id, scenarios) %>%
    mutate(KW_Normative = na.approx(KW_Normative_temp,
                                    maxgap = 1,
                                    rule = 1))
  
  kim003_interpolation <- subj_beliefs %>%
    rbind.data.frame(kim003_interpolation)
  #print(kim003_interpolation)
}

# # how many scenarios are there for each subject in kim003_interpolation dataframe?
# kim003_interpolation %>% filter(paper_id=="2016Kim003" & treatment_id == "2016Kim003_7") %>% 
#   group_by(subject_id) %>% 
#   summarise(n_scen=length(scenarios)) %>%
#   group_by(n_scen) %>%
#   summarise(n_subjs = length(subject_id))

# # how many scenarios are there for each subject in beliefs datafreme?
# beliefs %>% filter(paper_id=="2016Kim003" & treatment_id == "2016Kim003_7") %>% 
#   group_by(subject_id) %>% 
#   summarise(n_scen=length(scenarios)) %>%
#   group_by(n_scen) %>%
#   summarise(n_subjs = length(subject_id))

# dataset to plot consistency
df_consistency_beliefs <- beliefs %>%
  select(paper_id, treatment_id, subject_id, scenarios, KW_Normative) %>%
  filter(treatment_id %in% levels(as.factor(master$treatment_id))) %>%
  filter(paper_id != "2016Kim003") %>%
  rbind.data.frame(kim003_interpolation %>% select(-KW_Normative_temp)) %>%
  merge.data.frame(master %>%
                     subset.data.frame(select = c(treatment_id,
                                                  max_sigma)),
                   by="treatment_id") 
# %>%
#   group_by(treatment_id, scenarios) %>%
#   summarise(sd = sd(KW_Normative),
#             max_sigma = max_sigma,
#             appropriateness = sum(KW_Normative)) %>%
#   mutate(consistency = 1-(sd/max_sigma))

scenarios_w_max_appropriateness <- beliefs %>%
  group_by(treatment_id, scenarios) %>%
  summarise(KW=mean(KW_Normative)) %>%
  summarise(scenarios=scenarios[which(KW==max(KW))])

output <- merge.data.frame(scenarios_w_max_appropriateness,
                           df_consistency_beliefs,
                           all.x = T,
                           by=c("treatment_id", "scenarios"))

# # are there the same subjects between output and beliefs?
# o <- output %>% group_by(treatment_id) %>% summarise(n_o=n())
# beliefs %>% filter(scenarios==0) %>% group_by(treatment_id) %>% summarise(n_b=n()) %>% merge.data.frame(o) %>% mutate(test=ifelse(n_b-n_o==0,"ok","n"))
```


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
ggplot(output,
       aes(x=treatment_id,
           y=KW_Normative)) +
  geom_boxplot() +
  labs(title="Distribution of appropriateness of most appropriate action (norm)") +
  xlab("Paper") +
  ylab("Appropriateness")

ggplot(output,
       aes(x=KW_Normative)) +
  geom_density() +
  facet_wrap(~treatment_id, ncol=2)
```

## Specificity

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

df_specificity_per_subject <- beliefs %>% 
  group_by(subject_id) %>% 
  mutate(n_actions_positive = sum(KW_Normative>0), 
         n_actions_negative=sum(KW_Normative<=0), 
         specificity = n_actions_negative/n_actions_positive)

#box plot of specificity
ggplot(df_specificity_per_subject, 
       aes(x=treatment_id, 
           y=specificity)) + 
  geom_boxplot() + 
  labs(title="Boxplot of specificity per paper") +
  xlab("Paper") + 
  ylab("Specificity")

```


# Individual-level analyses {.tabset}

## Standard

$U_{ik} = \alpha \pi_k + \beta A_k + \epsilon_{ik}$

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", include=FALSE}
utility_df_long <- df_consistency_beliefs %>% 
  group_by(subject_id) %>% 
  mutate(n_actions_positive = sum(KW_Normative>=0), 
         n_actions_negative=sum(KW_Normative<0), 
         specificity = n_actions_negative/n_actions_positive)

mean_beliefs <- df_consistency_beliefs %>%
  group_by(treatment_id, scenarios) %>%
  summarise(mean_app = mean(KW_Normative),
            sd_app = sd(KW_Normative))

utility_df_treatment <- choices %>%
  merge.data.frame(mean_beliefs) %>%
  arrange(paper_id,treatment_id,subject_id,scenarios) %>%
  mutate(payoff = endowment - scenarios) %>%
  relocate(paper_id,treatment_id,subject_id,scenarios,choice,A,endowment,
           payoff,mean_app,sd_app)

betas_standard_logit <- data.frame(paper = NA, alpha=NA, beta=NA, SE_alpha=NA, SE_beta=NA, MRS=NA)

# mlogit standard
model_list <- list()
n_model = 1
for (i in levels(as.factor(utility_df_treatment$treatment_id))) {
  model=mclogit::mclogit(cbind(A,choice)~ payoff + mean_app, data=utility_df_treatment%>% 
                           filter(treatment_id==i))
  model_list[[n_model]] = model
  n_model = n_model +1

  betas_standard_logit <- betas_standard_logit %>% 
    rbind.data.frame(data.frame(paper = i, 
                                alpha = as.numeric(model$coefficients[1]),
                                beta=as.numeric(model$coefficients[2]),
                                SE_alpha=coef(summary(model))[1, "Std. Error"],
                                SE_beta=coef(summary(model))[2, "Std. Error"],
                                MRS = 2*as.numeric(model$coefficients[2])/as.numeric(model$coefficients[1])))
}

opts <- options(knitr.kable.NA = "")
kbl(betas_standard_logit,
    digits = 4, 
    booktabs = T, 
    align = "lcccc", 
    centering = F, 
    caption="Coefficients for standard model") %>%
  kable_styling(position = "left", 
                full_width = F) %>%
  column_spec(1, bold = T)
```


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
tab_model(model_list, dv.labels = levels(as.factor(utility_df_treatment$treatment_id)), show.aic = T, show.loglik = T)
```


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", include=FALSE}
ggplot(betas_standard_logit %>% filter(!(is.na(beta))) %>% arrange(beta), aes(x=beta,y=paper)) + 
  geom_point() + 
  geom_errorbar(aes(xmin=beta-2*SE_beta,xmax=beta+2*SE_beta))
```

## With Standard Deviation

$U_{ik} = \alpha \pi_k + \beta A_k + \delta C_k + \epsilon_{ik}$

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
betas_cons_logit <- data.frame(paper = NA, alpha=NA, beta=NA, delta=NA, SE_alpha=NA, SE_beta=NA, SE_delta=NA, MRS=NA)

# mlogit consistency
for (i in levels(as.factor(utility_df_treatment$treatment_id))) {
  model2=mclogit::mclogit(cbind(A,choice)~ payoff + mean_app * sd_app, data=utility_df_treatment%>% 
                           filter(treatment_id==i))
  
  betas_cons_logit <- betas_cons_logit %>% 
    rbind.data.frame(data.frame(paper = i, 
                                alpha = as.numeric(model2$coefficients[1]),
                                beta=as.numeric(model2$coefficients[2]),
                                delta=as.numeric(model2$coefficients[3]),
                                SE_alpha=coef(summary(model2))[1, "Std. Error"],
                                SE_beta=coef(summary(model2))[2, "Std. Error"],
                                SE_delta=coef(summary(model2))[3, "Std. Error"],
                                MRS = 2*as.numeric(model2$coefficients[2])/as.numeric(model2$coefficients[1])))
}

opts <- options(knitr.kable.NA = "")
kbl(betas_cons_logit,
    digits = 4, 
    booktabs = T, 
    align = "lcccc", 
    centering = F, 
    caption="Coefficients for model with std") %>%
  kable_styling(position = "left", 
                full_width = F) %>%
  column_spec(1, bold = T)

ggplot(betas_cons_logit %>% filter(!(is.na(beta))) %>% arrange(beta), aes(x=beta,y=paper)) + 
  geom_point() + 
  geom_errorbar(aes(xmin=beta-2*SE_beta,xmax=beta+2*SE_beta))

ggplot(betas_cons_logit %>% filter(!(is.na(delta))) %>% arrange(delta), aes(x=delta,y=paper)) + 
  geom_point() + 
  geom_errorbar(aes(xmin=delta-2*SE_delta,xmax=delta+2*SE_delta))
```


## Social preferences model

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", include=FALSE}
choices_per_social_model <- choices %>% mutate(payoff=endowment-scenarios,
                              other_payoff_ahead=ifelse(payoff>scenarios,payoff-scenarios,0),
                              other_payoff_behind=ifelse(payoff<scenarios,scenarios-payoff,0))

utility_df_treatment_2 <- choices_per_social_model %>%
  merge.data.frame(mean_beliefs) %>%
  arrange(paper_id,treatment_id,subject_id,scenarios) %>%
  relocate(paper_id,treatment_id,subject_id,scenarios,choice,A,endowment,
           payoff,mean_app,sd_app)

betas_standard_logit <- data.frame(paper = NA, rho=NA, sigma=NA, SE_rho=NA, SE_sigma=NA)

model_list2 <- list()
n_model2=1
# mlogit
for (i in levels(as.factor(utility_df_treatment_2$treatment_id))) {
  model2=mclogit::mclogit(cbind(A,choice)~ other_payoff_ahead + other_payoff_behind, data=utility_df_treatment_2%>% 
                           filter(treatment_id==i))
  model_list2[[n_model2]] = model2
  n_model2 = n_model2 +1
 
  
  # betas_cons_logit <- betas_cons_logit %>% 
  #   rbind.data.frame(data.frame(paper = i, 
  #                               rho = as.numeric(model2$coefficients[1]),
  #                               sigma=as.numeric(model2$coefficients[2]),
  #                               SE_rho=coef(summary(model2))[1, "Std. Error"],
  #                               SE_sigma=coef(summary(model2))[2, "Std. Error"]))
}

# opts <- options(knitr.kable.NA = "")
# kbl(betas_cons_logit,
#     digits = 4, 
#     booktabs = T, 
#     align = "lccc", 
#     centering = F, 
#     caption="Coefficients for model with std") %>%
#   kable_styling(position = "left", 
#                 full_width = F) %>%
#   column_spec(1, bold = T)
# 
# ggplot(betas_cons_logit %>% filter(!(is.na(sigma))) %>% arrange(sigma), aes(x=sigma,y=paper)) +
#   geom_point() +
#   geom_errorbar(aes(xmin=sigma-2*SE_sigma,xmax=sigma+2*SE_sigma))
# 
# ggplot(betas_cons_logit %>% filter(!(is.na(rho))) %>% arrange(rho), aes(x=rho,y=paper)) +
#   geom_point() +
#   geom_errorbar(aes(xmin=rho-2*SE_rho,xmax=rho+2*SE_rho))
```


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
tab_model(model_list2, dv.labels = levels(as.factor(utility_df_treatment_2$treatment_id)), show.aic = T, show.loglik = T)

```

## Demographic analysis {.tabset}

### Gender

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
utility_df_long <- df_consistency_beliefs %>% 
  group_by(subject_id) %>% 
  mutate(n_actions_positive = sum(KW_Normative>=0), 
         n_actions_negative=sum(KW_Normative<0), 
         specificity = n_actions_negative/n_actions_positive)

mean_beliefs <- df_consistency_beliefs %>%
  group_by(treatment_id, scenarios) %>%
  summarise(mean_app = mean(KW_Normative),
            sd_app = sd(KW_Normative))

utility_df_treatment_3 <- choices %>%
  merge.data.frame(mean_beliefs) %>%
  arrange(paper_id,treatment_id,subject_id,scenarios) %>%
  mutate(payoff = endowment - scenarios) %>%
  relocate(paper_id,treatment_id,subject_id,scenarios,choice,A,endowment,
           payoff,mean_app,sd_app) %>%
  filter(paper_id != "2018Her061")


# mlogit standard
model_list3 <- list()
n_model = 1
for (i in levels(as.factor(utility_df_treatment_3$treatment_id))) {
  print(i)
  model3=mclogit::mclogit(cbind(A,choice)~ payoff + mean_app*female, data=utility_df_treatment%>% 
                           filter(treatment_id==i))
  model_list3[[n_model]] = model3
  n_model = n_model +1
}

tab_model(model_list3, dv.labels = levels(as.factor(utility_df_treatment_3$treatment_id)), show.aic = T, show.loglik = T)
```
### Age

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
utility_df_long <- df_consistency_beliefs %>% 
  group_by(subject_id) %>% 
  mutate(n_actions_positive = sum(KW_Normative>=0), 
         n_actions_negative=sum(KW_Normative<0), 
         specificity = n_actions_negative/n_actions_positive)

mean_beliefs <- df_consistency_beliefs %>%
  group_by(treatment_id, scenarios) %>%
  summarise(mean_app = mean(KW_Normative),
            sd_app = sd(KW_Normative))

utility_df_treatment_4 <- choices %>%
  merge.data.frame(mean_beliefs) %>%
  arrange(paper_id,treatment_id,subject_id,scenarios) %>%
  mutate(payoff = endowment - scenarios) %>%
  relocate(paper_id,treatment_id,subject_id,scenarios,choice,A,endowment,
           payoff,mean_app,sd_app) %>%
  filter(paper_id != "2018Her061")


# mlogit standard
model_list4 <- list()
n_model = 1
for (i in levels(as.factor(utility_df_treatment_4$treatment_id))) {
  print(i)
  model4=mclogit::mclogit(cbind(A,choice)~ payoff + mean_app*age, data=utility_df_treatment%>% 
                           filter(treatment_id==i))
  model_list4[[n_model]] = model4
  n_model = n_model +1
}

tab_model(model_list4, dv.labels = levels(as.factor(utility_df_treatment_4$treatment_id)), show.aic = T, show.loglik = T)
```

