---
title: "Social Norms Meta"
output: 
  html_document:
    toc: True
    toc_float: True
---

# Analysis Treatment-level: All Games

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", include=FALSE}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(mclogit)
library(sjmisc)
library(ggrepel)
library(readxl)
library(ggpubr)
library(survival)
library(sjPlot)

setwd("../")

# read data 
master <- read.csv("File_DB/Output/Treatment.csv") %>% mutate(Delta_Avg = Avg_NE - Avg_coop,
                                                            Macro_game_type = ifelse(Game_type %in% c("DG","Donation Game"), "DG and Donation Game", Game_type)) %>% subset.data.frame(subset = PaperID !="2017Del037")

```

<br>

## HP1: Relation between norms and actions

<br>

<h4><i>Are norms and cooperation behavior related?</i></h4>

The content of the norm and behavior correlate positively.

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

cor.test(master$Avg_NE, master$Avg_coop, method= "spearman", exact = F)

ggplot(data=master, aes(x=Avg_NE, y=Avg_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Fig. 1: H1 : Correlation Between Average Cooperation and Norm (NE)") + stat_cor(method = "spearman") + xlab("Cooperation Norm (as % of endowment)") + ylab("Cooperation (% of endowment)")

ggplot(data=master, aes(x=Avg_NE, y=Avg_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Fig. 2: H1 : Correlation Between Average Cooperation and Norm (NE)") + facet_wrap(~Macro_game_type, ncol=3) + stat_cor(method = "spearman")

```

### Results
- Evidence from testing H1 shows that there is a positive and significant correlation between social expectations and cooperative behavior (Fig. 1).
- By splitting data by game type, there is evidence of positive and significant correlation in DG (and Donation game), while norms are not heterogeneous in other game types. 
- Hence, the analysis including all games possibly makes more sense here.

## HP2: Norm Uncertainty

<br>

- a. Does a higher norm variability lead to lower cooperation?
- b. Does a higher norm variability lead to higher cooperation variance?

<br>

to do so we computed VAR NE as ...

<h4><i>a. Does a higher norm variability lead to lower cooperation?</i></h4>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

cor.test(master$Var_NE, master$Avg_coop, method= "spearman", exact = F)

ggplot(data=master, aes(x=Var_NE, y=Avg_coop)) + geom_point() + geom_smooth(method="lm") + ggtitle("Fig. 3 H2a : Correlation Between Average Cooperation and Norm Variance (NE)") + stat_cor(method = "spearman") 

ggplot(data=master, aes(x=Var_NE, y=Avg_coop)) + geom_point() + ggtitle("Fig. 4 H2a : Correlation Between Average Cooperation and Norm Variance (NE)") + facet_wrap(~Macro_game_type, ncol=3) + stat_cor(method = "spearman") + geom_smooth(method="lm")

```
<br>

<h4><i>b. Does a higher norm variability lead to higher cooperation var.?</i></h4>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

cor.test(master$Var_NE, master$Var_coop, method= "spearman", exact = F)
ggplot(data=master, aes(x=Var_NE, y=Var_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Fig. 5 H2b : Correlation Between Variance Cooperation and Norm (NE)")

ggplot(data=master, aes(x=Var_NE, y=Var_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Fig. 6 H2b : Correlation Between Variance Cooperation and Norm (NE)") + facet_wrap(~Macro_game_type) + stat_cor(method = "spearman")

```

<br>

## HP3 : Is compliance related to norm strength?

$$Strength = {1 \over NE_{Specificity}+NE_{Consistency}}$$
where 

specificity is  and consistency accounts for the variability among appropriateness scores of individuals with respect to the norm in the game (e.g., if the norm in the game is 5, we compute the standard deviation among the appropriateness scores )

We compute compliance as delta XXX


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

master = master %>% mutate(Norm_Strength = 1/(sqrt(Var_NE)+Sd_Avg_NE)) %>% mutate(Delta_new = (Avg_NE-Avg_coop))

cor.test(master$Norm_Strength, master$Delta_new, method= "spearman", exact = F)

ggplot(data=master, aes(x=Norm_Strength, y=Delta_new)) + geom_point() + geom_smooth(method = "lm") + stat_cor(method = "spearman")

ggplot(data=master, aes(x=Norm_Strength, y=Delta_new)) + geom_point() + geom_smooth(method = "lm")+ facet_wrap(~Macro_game_type, ncol=3) + stat_cor(method = "spearman")# + geom_text(aes(label=PaperID))

```

<b>Summary of Norm strength</b>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
summary(master$Norm_Strength)
```

<b>Distribution</b>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
ggplot(data=master, aes(x=Norm_Strength)) +
geom_histogram() + ggtitle("Histogram of Norm Strength") + xlab("Strength Norm") + facet_wrap(~Macro_game_type)

```

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
DG <- master %>% subset.data.frame(Game_type=="DG" & Choice_Method== "Direct")
DG_UG <- master %>% subset.data.frame(Game_type=="DG"|Game_type=="UG")
UG <- master %>% subset.data.frame(Game_type=="UG")
```

# Individual-level analysis

## Analysis plan
Here we estimate a random utility model.
We split our individual-level analysis into 2 steps: 

1. we estimate the utility function when beliefs and actions are elicited for the same subject
2. we estimate the utility function when beliefs and actions are elicited using distinct subjects


For 1., the model we estimate is the following:

$U_{ij} = \alpha \pi_j + \beta S_{ij}$ 

while for 2., we use $S_j=\Sigma S_{ij}/N$ from the external sample with which social norms were elicited.

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
beliefs <- read.csv("../File_DB/Output/Subjects_beliefs.csv", sep = ",")
choices <- read.csv("../File_DB/Output/Subjects_choices.csv", sep = ",")
```

## Within-subjects Design
```{r}
beliefs_w <- beliefs %>% subset.data.frame(subset = Design=="Within")
choices_w <- choices %>% subset.data.frame(subset = Design=="Within")
individual_db_w <- merge.data.frame(choices_w, beliefs_w)
```


### 2020Bas115
```{r}
Bas115 = individual_db_w %>% subset.data.frame(paper_id=="2020Bas115") %>% mutate(payoff=endowment-scenarios)
clogit.bas <- clogit(A~ payoff + KW_Normative + strata(subject_id), data = Bas115)
summary(clogit.bas)
```

#### issues: 
- 345 subjects but only 342 in preliminary analysis: check if subjects are the same and scenarios are all for everyone

## Between 
```{r}
beliefs_b <- beliefs %>% subset.data.frame(subset = Design=="Between") %>% group_by(paper_id, scenarios) %>% summarise(KW_Normative = mean(KW_Normative))
choices_b <- choices %>% subset.data.frame(subset = Design=="Between")%>% mutate(payoff=endowment-scenarios)
individual_db_b <- merge.data.frame(choices_b, beliefs_b)

```

```{r}
between <- clogit(A~ payoff + KW_Normative + strata(subject_id, treatment_id, paper_id), data = individual_db_b)
betas=between$coefficients
summary(between)
sigma=sqrt(between$var) # diagonal is variance; others are covariance
plot_model(between)
```

### 2016Kim003
```{r}
Kim003 = individual_db_b %>% subset.data.frame(paper_id=="2016Kim003") %>% mutate(payoff=endowment-scenarios)
clogit.kim <- clogit(A~ payoff + KW_Normative + strata(subject_id, treatment_id, paper_id), data = Kim003)
summary(clogit.kim)
betas=clogit.kim$coefficients
sigma=sqrt(clogit.kim$var) # diagonal is variance; others are covariance
plot_model(model = clogit.kim, title = "2016Kim003: Conditional Logit Model")

```

### 2018Her061
```{r}
Her061 = individual_db_b %>% subset.data.frame(paper_id=="2018Her061") %>% mutate(payoff=endowment-scenarios)
clogit.her <- clogit(A~ payoff + KW_Normative + strata(subject_id, treatment_id, paper_id), data = Her061)
summary(clogit.her)
betas=clogit.her$coefficients
sigma=sqrt(clogit.her$var) # diagonal is variance; others are covariance
plot_model(model = clogit.her, title = "2018Her061: Conditional Logit Model")
```

### 2019Cha026
``` {r}
Cha026 = individual_db_b %>% subset.data.frame(paper_id=="2019Cha026") %>% mutate(payoff=endowment-scenarios)
clogit.cha <- clogit(A~ payoff + KW_Normative + strata(subject_id, treatment_id, paper_id), data = Cha026)
summary(clogit.cha)
betas=clogit.cha$coefficients
sigma=sqrt(clogit.cha$var) # diagonal is variance; others are covariance
plot_model(model = clogit.cha, title = "2019Cha026: Conditional Logit Model")
```




