---
title: "Social Norms Meta"

output: 
  html_document:
    toc: true
    toc_float: true
---

# Analysis Treatment-level: All Games

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, include=FALSE}

library(ggplot2)
library(tidyverse)
library(mclogit)
library(sjmisc)
library(ggrepel)
library(readxl)

setwd("C:/Users/stefa/Documenti/CNR/GitHub/Social_norm_meta_analysis/")

# read data 
master <- read.csv("File_DB/Output/Treatment.csv") %>% mutate(Delta_Avg = Avg_NE - Avg_coop, Strength_N = Delta_Avg/Sd_Avg_NE)
DG <- master %>% subset.data.frame(Game_type=="DG" & Choice_Method== "Direct")
DG_UG <- master %>% subset.data.frame(Game_type=="DG"|Game_type=="UG")
UG <- master %>% subset.data.frame(Game_type=="UG")

```

## HP1: Relation between norms and actions: Are stronger norms related with higher cooperation?

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}

cor.test(master$Avg_coop, master$Avg_NE, method= "spearman", exact = F)
ggplot(data=master, aes(x=Avg_NE, y=Avg_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("H1 : correlation between average cooperation and norm (NE)")

```

## HP2: Norm Uncertainty
- a. Does a higher norm variability lead to lower cooperation?
- b. Does a higher norm variability lead to higher cooperation var.?


### a. Does a higher norm variability lead to lower cooperation?

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}

cor.test(master$Avg_coop, master$Strength_N, method= "spearman", exact = F)
ggplot(data=master, aes(x=Avg_NE, y=Avg_coop, color=Game_type)) + geom_point() + geom_smooth() + ggtitle("H2a : correlation between average cooperation and norm (NE)")
```


### b. Does a higher norm variability lead to higher cooperation var.?

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}

cor.test(master$Var_coop, master$Strength_N, method= "spearman", exact = F)
ggplot(data=master, aes(x=Var_NE, y=Var_coop, color=Game_type)) + geom_point() + geom_smooth() + ggtitle("H2b : correlation between variance cooperation and norm (NE)")

```

## HP3 : Norm Strength
### Does higher norm strength lead to higher norm compliance?


**How did we compute Strength index?**

$$Strength = {Delta_{avg} \over NE_{sd}}$$
where:

- $Delta_{avg} = NE_{avg} - Coop_{avg}$
- $NE_{sd}$ is the standard deviation of means of KW appropriateness score (for each scenarios)
 
 
**Summary of Norm strength**
**Distribution**
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}
summary(master$Strength_N)
```

**Distribution**

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}
hist(master$Strength_N, breaks = 20, main = "Histogram of Strength Norm", xlab = "Strength Norm")
```


**Results**

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}
cor.test(DG$Delta_Avg, DG$Strength_N, method= "spearman", exact = F)
ggplot(data=DG, aes(x=Strength_N, y=Delta_Avg)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Does higher norm strength lead to higher norm compliance?")

```


# Analysis Treatment-level: Dictator Game

## H1
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}

cor.test(DG$Avg_coop, DG$Avg_NE, method= "spearman", exact = F)
ggplot(data=DG, aes(x=Avg_NE, y=Avg_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("H1 : correlation between average cooperation and norm (NE) \n DG only")
```

## H2a : correlation between average cooperation and norm (NE)
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}

cor.test(DG$Avg_coop, DG$Strength_N, method= "spearman", exact = F)
ggplot(data=DG, aes(x=Strength_N, y=Avg_coop)) + geom_point() + geom_smooth() + ggtitle("H2a : correlation between average cooperation and norm (NE) \n DG only")
```

## H2b : correlation between variance cooperation and norm (NE)
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}
      
cor.test(DG$Var_coop, DG$Strength_N, method= "spearman", exact = F)
ggplot(data=DG, aes(x=Strength_N, y=Var_coop, color=Game_type)) + geom_point() + geom_smooth() + ggtitle("H2b : correlation between variance cooperation and norm (NE) \n DG only")
```

### H3
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE}

cor.test(DG$Avg_coop, DG$Strength_N, method= "spearman", exact = F)
ggplot(data=DG, aes(x=Strength_N, y=Avg_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("H3 \n DG only")
```

# INDIVIDUAL-LEVEL ANALYSIS
```{r}
setwd("C:/Users/stefa/Documenti/CNR/GitHub/Social_norm_meta_analysis/")
beliefs <- read.csv("File_DB/Output/Subjects_beliefs.csv", sep = ",")
choices <- read.csv("File_DB/Output/Subjects_choices.csv", sep = ",")
```

## Within-subjects Design

## issues: 
### - 345 subjects but only 342 in preliminary analysis: check if subjects are the same and scenarios are all for everyone

beliefs_w <- beliefs %>% subset.data.frame(subset = Design=="Within")
choices_w <- choices %>% subset.data.frame(subset = Design=="Within")
individual_db_w <- merge.data.frame(choices_w, beliefs_w)

# prelim analysis all together
model_1 <- mclogit(cbind(A,scenarios)~KW_Normative,data=individual_db_w)

model_2017Del037 <- mclogit(cbind(A,scenarios)~KW_Normative,data=individual_db_w %>% 
                            subset.data.frame(subset = paper_id =="2017Del037"))

model_2020Bas115 <- mclogit(cbind(A,scenarios)~KW_Normative,data=individual_db_w %>% 
                              subset.data.frame(subset = paper_id=="2020Bas115"))

tab_model(model_1, model_2017Del037, 
          model_2020Bas115, 
          dv.labels = c("general model","Del037_model_1","2020Bas115"))

plot_models(model_1, model_2017Del037, 
          model_2020Bas115)
