---
title: "Social Norms Meta"
output: 
  html_document:
    toc: True
    toc_float: True
---

# Analysis Treatment-level: All Games

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", include=FALSE}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(mlogit)
library(sjmisc)
library(ggrepel)
library(readxl)
library(ggpubr)
library(survival)
library(sjPlot)
library(kableExtra)
library(car)
library(DT)
library(zoo)

setwd("../")

# read data 
master <- read.csv("File_DB/Output/Treatment.csv") %>% 
  mutate(Macro_game_type = ifelse(Game_type %in% c("DG","Donation Game"), "DG and Donation Game", Game_type), SD_NE=sqrt(Var_NE)) %>% 
  subset.data.frame(subset = !(Standard_game %in% c("N")))

```

<br>

## HP1: Relation between norms and actions

<br>

<h4><i>Are norms and cooperation behavior related?</i></h4>

The content of the norm and behavior correlate positively.

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

cor.test(master$Avg_NE, master$Avg_coop, method= "spearman", exact = F)

ggplot(data=master, aes(x=Avg_NE, y=Avg_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Fig. 1: H1 : Correlation Between Average Cooperation and Norm (NE)") + stat_cor(method = "spearman") + xlab("Cooperation Norm (as % of endowment)") + ylab("Cooperation (% of endowment)")

ggplot(data=master, aes(x=Avg_NE, y=Avg_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Fig. 2: H1 : Correlation Between Average Cooperation and Norm (NE)") + facet_wrap(~Macro_game_type, ncol=3) + stat_cor(method = "spearman")

```

### Results
- Evidence from testing H1 shows that there is a positive and significant correlation between social expectations and cooperative behavior (Fig. 1).
- By splitting data by game type, there is evidence of positive and significant correlation in DG (and Donation game), while norms are not heterogeneous in other game types. 
- Hence, the analysis including all games possibly makes more sense here.


<br>

## HP2 : Is compliance related to norm strength?

We compute norm strength as:

$$Strength = {NE_{Consistency}+NE_{Specificity}}$$

where:

* $NE_{Specificity} = \frac{{\sum_{i=1}^{N-1} max(KW)-KW_i}}{(N-1)[max(KW)-min(KW)]}$

* $NE_{Consistency} = {\sigma_{N} \over max(\sigma_{N})}$

We compute compliance as $Delta = NE_{avg}-Coop_{avg}$

<b>Summary of computed variables</b>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
# specificity = mean of max deviation
# consistency = sqrt(Var_NE)

master = master %>% mutate(consistency=sqrt(Var_NE)/max_sigma,
                           Norm_Strength = sqrt(Var_NE)/max_sigma + specificity,
                           Delta = (Avg_NE-Avg_coop))
```


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
summary(master$Norm_Strength)
summary(master$specificity)
summary(master$consistency)
```

<b>Distribution</b>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
ggplot(data=master%>% subset.data.frame(Choice_Method!="OnlyNorms"), aes(x=Norm_Strength)) +
geom_histogram(bins = 7, col=I("black")) + ggtitle("Histogram of Norm Strength") + xlab("Strength Norm") + facet_wrap(~Game_type)
```
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
cor.test(master$consistency, master$Delta, method= "spearman", exact = F)

ggplot(data=master%>% subset.data.frame(Choice_Method!="OnlyNorms"), aes(x=consistency, y=Delta)) + geom_point() + geom_smooth(method = "lm") + stat_cor(method = "spearman") #geom_text(aes(label=PaperID))

ggplot(data=master%>% subset.data.frame(Choice_Method!="OnlyNorms"), aes(x=consistency, y=Delta)) + geom_point() + geom_smooth(method = "lm")+ facet_wrap(~Macro_game_type, ncol=3) + stat_cor(method = "spearman")# + geom_text(aes(label=PaperID))

```

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
cor.test(master$specificity, master$Delta, method= "spearman", exact = F)

ggplot(data=master%>% subset.data.frame(Choice_Method!="OnlyNorms"), aes(x=specificity, y=Delta)) + geom_point() + geom_smooth(method = "lm") + stat_cor(method = "spearman") #geom_text(aes(label=PaperID))

ggplot(data=master%>% subset.data.frame(Choice_Method!="OnlyNorms"), aes(x=specificity, y=Delta)) + geom_point() + geom_smooth(method = "lm")+ facet_wrap(~Macro_game_type, ncol=3) + stat_cor(method = "spearman")# + geom_text(aes(label=PaperID))

```
  
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
cor.test(master$Norm_Strength, master$Delta, method= "spearman", exact = F)

ggplot(data=master%>% subset.data.frame(Choice_Method!="OnlyNorms"), aes(x=Norm_Strength, y=Delta)) + geom_point() + geom_smooth(method = "lm") + stat_cor(method = "spearman") #geom_text(aes(label=PaperID))

ggplot(data=master%>% subset.data.frame(Choice_Method!="OnlyNorms"), aes(x=Norm_Strength, y=Delta)) + geom_point() + geom_smooth(method = "lm")+ facet_wrap(~Macro_game_type, ncol=3) + stat_cor(method = "spearman")# + geom_text(aes(label=PaperID))

```


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
DG <- master %>% subset.data.frame(Game_type=="DG" & Choice_Method!= "OnlyNorms")
DG_UG <- master %>% subset.data.frame(Game_type=="DG"|Game_type=="UG")
UG <- master %>% subset.data.frame(Game_type=="UG"& Choice_Method!= "OnlyNorms")
```

## HP3: Effect of punishment on norms and actions

### Cooperation, Delta and Strength Comparison between DG and UG

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
hp4_mean <- master %>% 
  subset.data.frame(subset = Game_type %in% c("DG", "UG")&Choice_Method != "OnlyNorms") %>%
  group_by(Game_type) %>% 
  summarise(Coop = mean(Avg_coop, na.rm = T), 
            Avg_Norm = mean(Avg_NE, na.rm = T), 
            Delta = mean(Delta, na.rm = T), 
            Strength = mean(Norm_Strength, na.rm = T),
            n = n()) %>% 
  arrange(Game_type)

master_test <- master %>% subset.data.frame(select = c(Game_type, Avg_coop, Avg_NE, Delta, Norm_Strength, Macro_game_type, Sd_Avg_NE, Var_NE), subset = Game_type %in% c("DG", "UG"))

wilc_delta = wilcox.test(Delta ~ Macro_game_type, data=master_test)
wilc_strength = wilcox.test(Norm_Strength ~ Macro_game_type, data = master_test)
wilc_coop = wilcox.test(Avg_coop ~ Macro_game_type, data = master_test)
wilc_norm = wilcox.test(Avg_NE ~ Macro_game_type, data = master_test)

hp4plus_mean <- hp4_mean %>% add_row(Game_type = "Difference (M.W.W. p-value)", Coop = wilc_coop$p.value, Avg_Norm = wilc_norm$p.value, Delta = wilc_delta$p.value, Strength = wilc_strength$p.value)
```

We test the hypothesis whether :

* **Cooperation** ($Coop_{avg}$) in DG and Donation Game is lower then UG.

  + The p-value of Mann-Whitney-Wilcoxon Test is `r round(wilc_coop$p.value, digits = 4)`, therefore we *can* reject the null hypothesis (at .05 significance level).

* **Normative Expectation** ($NE_{avg}$) in DG and Donation Game is lower then UG.

  + The p-value of Mann-Whitney-Wilcoxon Test is `r round(wilc_norm$p.value, digits = 4)`, therefore we *can't* reject the null hypothesis (at .05 significance level).
  
* **Delta** in DG and Donation Game is lower then UG.
  + *Delta* is computed as $NE_{avg}-Coop_{avg}$ 
  + The p-value of Mann-Whitney-Wilcoxon Test is `r round(wilc_delta$p.value, digits = 4)`, therefore we *can* reject the null hypothesis (at .05 significance level).
  
* **Norm Strength** in DG and Donation Game is lower then UG.

  + The p-value of Mann-Whitney-Wilcoxon Test is `r round(wilc_strength$p.value, digits = 4)`, therefore we *can't* reject the null hypothesis (at .05 significance level).
  

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
opts <- options(knitr.kable.NA = "")
kbl(hp4plus_mean, digits = 4, booktabs = T, align = "lccccc", centering = F, caption = "Average and Mann-Whitney-Wilcoxon Test") %>%
  kable_styling(position = "left", full_width = F) %>%
  column_spec(1, bold = T) %>%
  row_spec(3, bold = T, color = "white", background = "#6c757d")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
# hp4_sd <- master %>% 
#   subset.data.frame(subset = Macro_game_type %in% c("DG and Donation Game", "UG")) %>%
#   group_by(Macro_game_type) %>% 
#   summarise(Coop = sd(Avg_coop, na.rm = T), 
#             Avg_Norm = sd(Avg_NE, na.rm = T), 
#             Delta = sd(Delta, na.rm = T), 
#             Strength = sd(Norm_Strength, na.rm = T),
#             n = n()) %>% 
#   arrange(Macro_game_type)
# 
# opts <- options(knitr.kable.NA = "")
# kbl(hp4_sd, digits = 4, booktabs = T, align = "lccccc", centering = F, caption = "Standard Deviation") %>%
#   kable_styling(position = "left", full_width = F) %>%
#   column_spec(1, bold = T)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
hp4_SP_CS <- master %>% 
  subset.data.frame(subset = Game_type %in% c("DG", "UG")) %>%
  group_by(Game_type) %>% 
  summarise(Specificity = mean(1/(Sd_Avg_NE), na.rm = T), 
            Consistency = mean(1/(sqrt(Var_NE)), na.rm = T)) %>% 
  arrange(Game_type)

F_test_spec <- wilcox.test(1/(master_test$Sd_Avg_NE) ~ master_test$Game_type)
F_test_cons <- wilcox.test(1/(sqrt(master_test$Var_NE)) ~ master_test$Game_type)

hp4plus_SP_CS <- hp4_SP_CS %>% 
  add_row(Game_type = "Difference (Wilcoxon p-value)", Specificity = F_test_spec$p.value, Consistency = F_test_cons$p.value)

opts <- options(knitr.kable.NA = "")
kbl(hp4plus_SP_CS, digits = 4, booktabs = T, align = "lcc", centering = F, caption = "Consistency e Specificity") %>%
  kable_styling(position = "left", full_width = F) %>%
  column_spec(1, bold = T) %>%
  row_spec(3, bold = T, color = "white", background = "#6c757d")

ggarrange(ggplot(master_test) + geom_density(aes(color = Game_type, x=log(1/Sd_Avg_NE))) + xlab("Specificity"),
ggplot(master_test) + geom_density(aes(color = Game_type, x=log(1/sqrt(Var_NE)))) + xlab("Consistency"), common.legend = T)

```



# Individual-level analysis {.tabset}

## Standard Utility framework {.tabset}
Here we estimate a random utility model using a conditional logit model (McFadden 1975).
We split our individual-level analysis into 2 steps:

1. *Within subject design belief elicitation*: we estimate the utility function when beliefs and actions are elicited for the same subject
2. *Between subject design belief elicitation*: we estimate the utility function when beliefs and actions are elicited using distinct subjects


For 1., the model we estimate is the following:

<center>
$U_{ij} = \alpha \pi_j + \beta S_{ij}$ 
</center>

<br>
while for 2., we use $S_j=\Sigma S_{ij}/N$ from the external sample with which social norms were elicited. Hence the model becomes:

<center>
$U_{ij} = \alpha \pi_j + \beta S_{j}$ 
</center>

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
beliefs <- read.csv("../File_DB/Output/Subjects_beliefs.csv", sep = ",")
choices <- read.csv("../File_DB/Output/Subjects_choices.csv", sep = ",")
dataframe_betas <- data.frame(ID=NA, t=NA, game=NA,alpha=NA, beta=NA,SE_alpha=NA,SE_beta=NA)
i=0
```

### Within-subjects Design {.tabset}
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
beliefs_w <- beliefs %>% subset.data.frame(subset = Design=="Within") #%>% subset.data.frame(select = c(paper_id,treatment_id,subject_id,scenarios,KW_Normative,Game_type))
choices_w <- choices %>% subset.data.frame(subset = Design=="Within") #%>% subset.data.frame(select = c(paper_id,treatment_id,subject_id,scenarios,A,choice,Game_type, endowment))
individual_db_w <- choices_w %>% merge.data.frame(beliefs_w)
```


#### 2020Bas115

DG - Treatment 1 ("Social")

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
Bas115_dg = individual_db_w %>% subset.data.frame(paper_id=="2020Bas115" & Game_type=="DG") %>% mutate(payoff=endowment-scenarios)
model <- clogit(A~ payoff + KW_Normative + strata(subject_id), data = Bas115_dg %>% subset.data.frame(subset = treatment_id =="2020Bas115_1a"))
summary(model)
dataframe_betas[i,] <- c("2020Bas115",1,"DG",model$coefficients["payoff"],model$coefficients["KW_Normative"],sqrt(model$var[1,1]),sqrt(model$var[2,2]))
```

DG - Treatment 2 ("Private")

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
model <- clogit(A~ payoff + KW_Normative + strata(subject_id), data = Bas115_dg %>% subset.data.frame(subset = treatment_id =="2020Bas115_2a"))
summary(model)
dataframe_betas[i,] <- c("2020Bas115",2, "DG",model$coefficients["payoff"],model$coefficients["KW_Normative"],sqrt(model$var[1,1]),sqrt(model$var[2,2]))
```

UG - Treatment 1 ("Social")

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
Bas115_ug = individual_db_w %>% subset.data.frame(paper_id=="2020Bas115" & Game_type=="UG") %>% mutate(payoff=endowment-scenarios)
model <- clogit(A~ payoff + KW_Normative + strata(subject_id), data = Bas115_ug %>% subset.data.frame(subset = treatment_id =="2020Bas115_1c"))
summary(model)
dataframe_betas[i,] <- c("2020Bas115",3,"UG",model$coefficients["payoff"],model$coefficients["KW_Normative"],sqrt(model$var[1,1]),sqrt(model$var[2,2]))
```

UG - Treatment 2 ("Private")

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
model <- clogit(A~ payoff + KW_Normative + strata(subject_id), data = Bas115_ug %>% subset.data.frame(subset = treatment_id =="2020Bas115_2c"))
summary(model)
dataframe_betas[i,] <- c("2020Bas115",4, "UG",model$coefficients["payoff"],model$coefficients["KW_Normative"],sqrt(model$var[1,1]),sqrt(model$var[2,2]))
```

### Between-subjects Design {.tabset}
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
beliefs_temp <- beliefs %>% subset.data.frame(subset = Design=="Between"&Game_type=="DG") %>% group_by(paper_id, scenarios) %>% summarise(KW_Normative = mean(KW_Normative, rm.na=T))

Kim003_interpolation <- beliefs_temp %>% subset.data.frame(paper_id == "2016Kim003") %>% 
  rbind.data.frame(data.frame(paper_id="2016Kim003", scenarios=seq(1,15,2), KW_Normative=NA)) %>% 
  ungroup() %>% arrange(scenarios) %>%
  mutate(KW_Normative = na.approx(KW_Normative, maxgap = 1, rule = 1))

beliefs_b <- beliefs_temp %>% merge.data.frame(Kim003_interpolation, all = T)
choices_b <- choices %>% subset.data.frame(subset = Design=="Between")%>% mutate(payoff=endowment-scenarios)
individual_db_b <- merge.data.frame(choices_b, beliefs_b)
```

#### 2016Kim003
For DG game

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
Kim003_dg = individual_db_b %>% subset.data.frame(paper_id=="2016Kim003"&Game_type=="DG") %>% mutate(payoff=endowment-scenarios) %>% subset.data.frame(subset = subject_id!="2016Kim003_7_2222")
clogit.kim_dg <- clogit(A~payoff+KW_Normative +strata(subject_id), data = Kim003_dg)
summary(clogit.kim_dg)
dataframe_betas[i,] <- c("2016Kim003",1,"DG",clogit.kim_dg$coefficients["payoff"],clogit.kim_dg$coefficients["KW_Normative"],sqrt(clogit.kim_dg$var[1,1]),sqrt(clogit.kim_dg$var[2,2]))
```


For UG game
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
Kim003_ug = individual_db_b %>% subset.data.frame(paper_id=="2016Kim003"&Game_type=="UG") %>% mutate(payoff=endowment-scenarios) %>% subset.data.frame(subject_id!="2016Kim003_8_1804" & subject_id!="2016Kim003_8_2411")
  

#mlogit.kim <- mlogit(A~payoff+KW_Normative|0, data = Kim003_m)
#summary(mlogit.kim)#$CoefTable[1,2] ### SUCA 2beta/alpha monetary trade off from -1 to 1 
clogit.kim_ug <- clogit(A~payoff+KW_Normative +strata(subject_id), data = Kim003_ug)
summary(clogit.kim_ug)
dataframe_betas[i,] <- c("2016Kim003",2,"UG",clogit.kim_ug$coefficients["payoff"],clogit.kim_ug$coefficients["KW_Normative"],sqrt(clogit.kim_ug$var[1,1]),sqrt(clogit.kim_ug$var[2,2]))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
# Kim003_m <- dfidx(Kim003_ug %>% mutate(scenarios=as.factor(scenarios)),
#             idx = c("subject_id","scenarios"), 
#             idpkg = "mlogit")
# mlogit.kim <- mlogit(A~payoff+KW_Normative|-1, data = Kim003_m, rpar = c(KW_Normative="n", payoff="n"))
# #summary(mlogit.kim)#$CoefTable[1,2] ### SUCA 2beta/alpha monetary trade off from -1 to 1 
# mxcl <- update(mlogit.kim, correlation=T)
# kw_n <- rpar(mxcl,"KW_Normative", norm="payoff")
# #summary(kw_n)
# p=fitted(mxcl,type = "parameters")
# ggplot(data.frame(betas=p[,2]), aes(x=betas)) + geom_density()
```

#### 2018Her061
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
Her061 = individual_db_b %>% subset.data.frame(paper_id=="2018Her061") %>% mutate(payoff=endowment-scenarios)
clogit.her <- clogit(A ~ payoff + KW_Normative + strata(subject_id), data=Her061)
summary(clogit.her)
dataframe_betas[i,] <- c("2018Her061",1,"DG",clogit.her$coefficients["payoff"],clogit.her$coefficients["KW_Normative"],sqrt(clogit.her$var[1,1]),sqrt(clogit.her$var[2,2]))
```


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
# Her061_m <- dfidx(Her061 %>% mutate(scenarios=as.factor(scenarios)),
#             idx = c("subject_id","scenarios"), 
#             idpkg = "mlogit")
# mlogit.her <- mlogit(A~ payoff + KW_Normative|0, data = Her061_m, rpar = c(payoff="n", KW_Normative="n"))
# mxcl <- update(mlogit.her, correlation=T)
# kw_n <- rpar(mxcl,"KW_Normative", norm="payoff")
# summary(mlogit.her)
# p=fitted(mxcl,type = "parameters")
# ggplot(data.frame(betas=p[,2]), aes(x=betas)) + geom_density()
# mean(data.frame(betas=p[,2])$betas, na.rm = T)
```

#### 2019Cha026

Treatment 1

``` {r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
Cha026 = individual_db_b %>% subset.data.frame(paper_id=="2019Cha026") %>% mutate(payoff=endowment-scenarios)
#Cha026_m <- dfidx(Cha026 %>% mutate(scenarios=as.factor(scenarios)),
#            idx = c("subject_id","scenarios"), 
#            idpkg = "mlogit")

clogit.cha_1 <- clogit(A~ payoff + KW_Normative + strata(subject_id), data = Cha026%>% subset.data.frame(treatment_id=="2019Cha026_1"))
summary(clogit.cha_1)
#mlogit.cha <- mlogit(A~ 0+payoff + KW_Normative, data = Cha026_m)
#summary(mlogit.cha)
dataframe_betas[i,] <- c("2019Cha026",1, "DG", clogit.cha_1$coefficients["payoff"],clogit.cha_1$coefficients["KW_Normative"],sqrt(clogit.cha_1$var[1,1]),sqrt(clogit.cha_1$var[2,2]))
```


Treatment 2

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
clogit.cha_2 <- clogit(A~ payoff + KW_Normative + strata(subject_id), data = Cha026%>% subset.data.frame(treatment_id=="2019Cha026_2"))
summary(clogit.cha_2)
dataframe_betas[i,] <- c("2019Cha026",2, "DG", clogit.cha_2$coefficients["payoff"],clogit.cha_2$coefficients["KW_Normative"],sqrt(clogit.cha_2$var[1,1]),sqrt(clogit.cha_2$var[2,2]))
```

### All papers results
```{r echo=F, message=FALSE, warning=FALSE}

allpaperdata <- dataframe_betas %>% 
  mutate_at(.vars = vars(alpha:SE_beta), as.numeric) %>% 
  mutate(MRS = 2*as.numeric(beta)/as.numeric(alpha)) 

averages <- allpaperdata %>% summarise_at(.vars = vars(alpha:SE_beta), mean)

allpaperdata <- allpaperdata %>% add_row(ID="Average",t= "",game="", alpha=averages$alpha, beta=averages$beta, SE_alpha=averages$SE_alpha, SE_beta=averages$SE_beta, MRS=2*averages$beta/averages$alpha)
  

opts <- options(knitr.kable.NA = "")
kbl(allpaperdata, digits = 2, booktabs = T, align = "lccccc", centering = F, caption = "Estimated Parameters") %>%
  kable_styling(position = "left", full_width = F) %>%
  column_spec(1, bold = T)

ggplot(allpaperdata %>% mutate(uniqueID=paste(ID,t,sep = "_t")) %>% arrange(beta), aes(x=beta,y=uniqueID,color=ID)) + 
  geom_point() + 
  geom_errorbar(aes(xmin=beta-2*SE_beta,xmax=beta+2*SE_beta))

```

## Augmented Utility framework {.tabset}

Here we augment the standard utility framework by including a measure of norm specificity either at the individual level and at the choice level depending on the nature of the data (between-subject elicitation or within-subject elicitation).


<center>
$U_{ij} = \alpha \pi_j + \beta S_{ij} + \eta S_{ij}*\sigma_i(S_{ij})$ 
</center>

where $\sigma(\cdot)$ is the standard deviation of $S_{ij}$ representing uncertainty around the norm.


<center>
$U_{ij} = \alpha \pi_j + \beta S_{j} + \eta S_{j}*\sigma_j(S_{ij})$ 
</center>


### Within-subjects elicitation {.tabset}

#### 2020Bas115

DG - T1
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=1
SDi= Bas115_dg %>% group_by(subject_id) %>% summarise(sdi=sd(KW_Normative))
Bas115_dg <- Bas115_dg %>% merge.data.frame(SDi)
model <- clogit(A~ payoff + KW_Normative+ KW_Normative:sdi + strata(subject_id), data = Bas115_dg%>% subset.data.frame(subset = treatment_id=="2020Bas115_1a"))
summary(model)
dataframe_betas_augmented <- data.frame(ID="2020Bas115",t=1,game_type="DG",alpha=model$coefficients["payoff"],
                                        beta=model$coefficients["KW_Normative"],
                                        gamma=model$coefficients["KW_Normative:sdi"],
                                        SE_alpha=sqrt(model$var[1,1]),
                                        SE_beta=sqrt(model$var[2,2]),
                                        SE_gamma=sqrt(model$var[3,3]), row.names = NULL
                                        )
```

DG - T2
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
model <- clogit(A~ payoff + KW_Normative+ KW_Normative:sdi + strata(subject_id), data = Bas115_dg%>% subset.data.frame(subset = treatment_id=="2020Bas115_2a"))
summary(model)
dataframe_betas_augmented[i,] <- c(ID="2020Bas115",t=2,game_type="DG",alpha=model$coefficients["payoff"],
                                        beta=model$coefficients["KW_Normative"],
                                        gamma=model$coefficients["KW_Normative:sdi"],
                                        SE_alpha=sqrt(model$var[1,1]),
                                        SE_beta=sqrt(model$var[2,2]),
                                        SE_gamma=sqrt(model$var[3,3])
                                        )

```

### Between-subjects elicitation {.tabset}

#### 2016Kim003

DG game
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
SDj= beliefs %>% group_by(paper_id, treatment_id, scenarios) %>% summarise(sdj=sd(KW_Normative))
i=i+1
Kim003_dg = Kim003_dg %>% merge.data.frame(SDj)
model <- clogit(A~payoff+KW_Normative + KW_Normative:sdj + strata(subject_id), data = Kim003_dg)
summary(model)
dataframe_betas_augmented[i,] <- c(ID="2016Kim003",t=1,game_type="DG",
                                   alpha=model$coefficients["payoff"],
                                        beta=model$coefficients["KW_Normative"],
                                        gamma=model$coefficients["KW_Normative:sdi"],
                                        SE_alpha=sqrt(model$var[1,1]),
                                        SE_beta=sqrt(model$var[2,2]),
                                        SE_gamma=sqrt(model$var[3,3]))
```

For UG game
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
SDj= Kim003_ug %>% group_by(scenarios) %>% summarise(sdj=sd(KW_Normative))
Kim003_ug = Kim003_ug %>% merge.data.frame(SDj)
model <- clogit(A~payoff+KW_Normative + KW_Normative*sdj + strata(subject_id), data = Kim003_ug)
summary(model)
dataframe_betas_augmented[i,] <- c(ID="2016Kim003",t=2,game_type="UG",alpha=model$coefficients["payoff"],
                                        beta=model$coefficients["KW_Normative"],
                                        gamma=model$coefficients["KW_Normative:sdi"],
                                        SE_alpha=sqrt(model$var[1,1]),
                                        SE_beta=sqrt(model$var[2,2]),
                                        SE_gamma=sqrt(model$var[3,3]))
```


## Individual analysis of norm compliance {.tabset}


### bas155
bas115_strenght <- Bas115 %>% group_by(subject_id) %>% summarise(specificity = sd(KW_Normative))
data_bas115 <- Bas115 %>% merge.data.frame(bas115_strenght)
data_bas115_m <- dfidx(data_bas115 %>% mutate(scenarios=as.factor(scenarios)),
            idx = c("subject_id","scenarios"), 
            idpkg = "mlogit")
summary(mlogit(A ~ payoff |KW_Normative|specificity , data=data_bas115_m))


# Appendix {.tabset}



## Effect of varibility on norms and actions

<br>

- a. Does a higher norm variability lead to lower cooperation?
- b. Does a higher norm variability lead to higher cooperation variance?

<br>

to do so we computed VAR_NE ($NE_{var}$) as:

$$ NE_{var} = \sigma^2_{i}(max\{\mu_j(NE)\}) $$

<h4><i>a. Does a higher norm variability lead to lower cooperation?</i></h4>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

cor.test(master$Var_NE, master$Avg_coop, method= "spearman", exact = F)

ggplot(data=master, aes(x=Var_NE, y=Avg_coop)) + geom_point() + geom_smooth(method="lm") + ggtitle("Fig. 3 H2a : Correlation Between Average Cooperation and Norm Variance (NE)") + stat_cor(method = "spearman") 

ggplot(data=master, aes(x=Var_NE, y=Avg_coop)) + geom_point() + ggtitle("Fig. 4 H2a : Correlation Between Average Cooperation and Norm Variance (NE)") + facet_wrap(~Macro_game_type, ncol=3) + stat_cor(method = "spearman") + geom_smooth(method="lm")

```

<br>

<h4><i>b. Does a higher norm variability lead to higher cooperation var.?</i></h4>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}

cor.test(master$Var_NE, master$Var_coop, method= "spearman", exact = F)
ggplot(data=master, aes(x=Var_NE, y=Var_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Fig. 5 H2b : Correlation Between Variance Cooperation and Norm (NE)")

ggplot(data=master, aes(x=Var_NE, y=Var_coop)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Fig. 6 H2b : Correlation Between Variance Cooperation and Norm (NE)") + facet_wrap(~Macro_game_type) + stat_cor(method = "spearman")

```

## Papers included
``` {r echo=F}
n_subjects_choice <- choices %>% subset.data.frame(A==1) %>% group_by(paper_id, treatment_id) %>% summarise(N_choices=length(A)) %>% rename(PaperID=paper_id) %>% mutate(TreatmentCode=str_split_fixed(treatment_id,"_",2)[,2]) %>% subset.data.frame(select = -c(treatment_id))

n_subjects_beliefs <- beliefs %>% group_by(subject_id) %>% filter(row_number()==1)%>%group_by(paper_id, treatment_id) %>% summarise(N_beliefs=length(scenarios))%>% rename(PaperID=paper_id) %>% mutate(TreatmentCode=str_split_fixed(treatment_id,"_",2)[,2]) %>% subset.data.frame(select = -c(treatment_id))

list_of_paper <- master %>% 
  mutate(data_type = ifelse(is.na(Avg_NE), "Actions", ifelse(is.na(Avg_coop), "Norms", "Both"))) %>% 
  group_by(data_type, PaperID, TreatmentCode, Game_type, Method_elicitation, Separate_sample_beliefs, Standard_game) %>% 
  summarise(n_treatments = n()) %>% merge.data.frame(n_subjects_choice, all.x = T) %>% merge.data.frame(n_subjects_beliefs, all.x = T)

opts <- options(knitr.kable.NA = "")
kbl(list_of_paper, digits = 4, booktabs = T, align = "lcccccc", centering = F, caption = "Ciao") %>%
  kable_styling(position = "left", full_width = F) %>%
  column_spec(1, bold = T)

datatable(master %>% subset.data.frame(select = c(PaperID, TreatmentCode, Game_type, Avg_coop, SD_NE, Sd_Avg_NE, Norm_Strength, Delta)),rownames = F) %>% formatRound(columns = c("Avg_coop", "Avg_coop", "SD_NE", "Sd_Avg_NE", "Norm_Strength", "Delta"), digits = 2)

```

## Conditional logit model (Overall model)
```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
i=i+1
between <-clogit(A~ payoff*paper_id + KW_Normative*paper_id + strata(subject_id), data = individual_db_b)
summary(between)
#dataframe_betas[i,] <- c("Avg. Between",between$coefficients["payoff"],between$coefficients["KW_Normative"],between$var[1,1],between$var[2,2])
```
